---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(ggplot2)
library(jsonlite)
library(stringr)
library(tidyr)
```


Select those that apply
```{r}
path = "/home/nitesh-jaswal/Study/Search/Project/yelp_dataset/"
tip.df = jsonlite::stream_in(file(description = paste0(path , "tip.json"), open = "r"))
user.df = jsonlite::stream_in(file(description = paste0(path , "user.json"), open = "r"))
business.df = jsonlite::stream_in(file(description = paste0(path , "business.json"), open = "r"))
review.df = jsonlite::stream_in(file(description = paste0(path , "review.json"), open = "r"))
checkin.df = jsonlite::stream_in(file(description = paste0(path , "checkin.json"), open = "r"))
```
Filter all reviews by city
```{r}
cityFilter <- function(city) {
  truncated_review_df = inner_join(filter(business.df, city == city), review.df , by = "business_id")
  return(truncated_review_df)
}

```


Returns unique length of the list or vector passed

```{r}
uniqueLength <- function(x) {
  return( x %>% unique() %>% length() )
}
```

Filter the users based on city

```{r}
# user.df = jsonlite::stream_in(file(description = paste0(path , "user.json"), open = "r"))
# truncated_review_df = cityFilter(city = "Toronto")
# truncated_review_df = truncated_review_df %>% rename("business_stars" = "stars.x" , "review_stars" = "stars.y")
# saveRDS(truncated_review_df, "/home/nitesh-jaswal/Study/Search/Project/toronoto_reviews_unfiltered_users.RDS")

truncated_review_df = readRDS("/home/nitesh-jaswal/Study/Search/Project/toronoto_reviews_unfiltered_users.RDS")
```

Filters users in a city based on their review_count and merge with reveiw.df
```{r}
filterCityUsersAndMerge <- function(k) {
  if(is.na(k)) {
    return(truncated_review_df)
  }
  else {
    user.df_truncated <- filter(user.df, review_count >= k)
    toronoto_reviews_filtered_users.df = inner_join(truncated_review_df,  user.df_truncated, by = "user_id")
    return(toronoto_reviews_filtered_users.df)
  }
}

```

K = 20
```{r}

# K = 20
toronoto_reviews_filtered_users.df = filterCityUsersAndMerge(20)

# Finds unique number of reviews
# toronoto_reviews_filtered_users.df$review_id %>% uniqueLength()
# toronoto_reviews_filtered_users.df$user_id %>% uniqueLength()
# toronoto_reviews_filtered_users.df$business_id %>% uniqueLength()

```
K = 40
```{r}
# K = 40
toronoto_reviews_filtered_users.df = filterCityUsersAndMerge(40)

# Finds unique number of reviews
toronoto_reviews_filtered_users.df$review_id %>% uniqueLength()
toronoto_reviews_filtered_users.df$user_id %>% uniqueLength()
toronoto_reviews_filtered_users.df$business_id %>% uniqueLength()

```
K - 60
```{r}
# K =60
toronoto_reviews_filtered_users.df = filterCityUsersAndMerge(60)

# Finds unique number of reviews
toronoto_reviews_filtered_users.df$review_id %>% uniqueLength()
toronoto_reviews_filtered_users.df$user_id %>% uniqueLength()
toronoto_reviews_filtered_users.df$business_id %>% uniqueLength()
```
K = 80
```{r}
# K =80
toronoto_reviews_filtered_users.df = filterCityUsersAndMerge(80)

# Finds unique number of reviews
toronoto_reviews_filtered_users.df$review_id %>% uniqueLength()
toronoto_reviews_filtered_users.df$user_id %>% uniqueLength()
toronoto_reviews_filtered_users.df$business_id %>% uniqueLength()
```

Clean column names and rows
```{r}
# K = 20 Selected

# View dataset conflicting column names
# toronoto_reviews_filtered_users.df %>% select(name.x, name.y, cool.x, cool.y, funny.x, funny.y, review_count.x, review_count.y, useful.x, useful.y) %>% View
# Clean dataset conflicting column names
toronoto_reviews_filtered_users.df = toronoto_reviews_filtered_users.df %>% rename("business_name" = "name.x", "user_name" = "name.y","business_cool" = "cool.x", "user_cool" = "cool.y", "business_funny" = "funny.x", "user_funny" = "funny.y", "business_review_count" = "review_count.x", "user_review_count" = "review_count.y", "business_useful" = "useful.x", "user_useful" = "useful.y")

# Remove featureless columns
toronoto_reviews_filtered_users.df <- toronoto_reviews_filtered_users.df %>% select(-city, -state, -postal_code, -latitude, -longitude, -is_open, -hours, -yelping_since)

# Clean NA from columns we might not care about
temp <-toronoto_reviews_filtered_users.df %>% select(-address, -business_name,-attributes, -elite, friends, -fans, -compliment_hot, -compliment_more,-compliment_profile,-compliment_cute,-compliment_list,-compliment_note,-compliment_plain,-compliment_cool,-compliment_funny,-compliment_writer,-compliment_photos) %>% drop_na
toronoto_reviews_filtered_users.df <-  left_join(temp, toronoto_reviews_filtered_users.df)

rm(list = "temp")
```

Filter businesses based on categories 
```{r}
# category_list = toronoto_reviews_filtered_users.df$categories %>% unlist %>% unique
# category_tokens_list = lapply(category_list, function(x) {
#   tokens =  strsplit(x, ",")
#   return(tokens)
# })

# category_tokens = category_tokens %>% unlist %>%  trimws %>% unique
# View(category_tokens)
flag = regexec("(Restaurants)|(Bar)|(Food)|(Cafe?s)|(Juice?s)|(Fast Food)|(Bakeries)", toronoto_reviews_filtered_users.df$categories, perl = TRUE) > -1
# toronoto_reviews_filtered_users_biz.df <- filter(toronto_reviews_filtered_users.df, categories == flag)

```

```{r}
# summary(toronoto_reviews_filtered_users.df$attributes$GoodForKids %>% as.factor)
```

Expand nested JSON and Dataframes
```{r}
attributes_df <- data.frame("business_id" = toronoto_reviews_filtered_users.df$business_id, toronoto_reviews_filtered_users.df$attributes)

attributes_df <- select(attributes_df, business_id, RestaurantsPriceRange2, BusinessParking, BikeParking, RestaurantsTakeOut, GoodForKids, OutdoorSeating, RestaurantsGoodForGroups, RestaurantsReservations, RestaurantsDelivery	, WiFi)

attributes_df <- unique(attributes_df)

attributeJSONParser <- function(x) {
  if(is.na(x)) {
    return(NA)
  }
  else {
    x <- gsub("'", "", x)
    # cat(x)
    x <- gsub("([\\w\\-]+)", "\"\\1\"", x, perl = TRUE)
    # cat(x)
    return( jsonlite::parse_json(x) %>% as.data.frame )
  }
}

attributes_df <- drop_na(attributes_df)

# review_id, review_stars, user_id, user_useful, user_cool, user_funny, elite, fans,

# Parse and append BusinessParkingJSON
temp <- lapply(attributes_df$BusinessParking, attributeJSONParser)
n_row = length(temp)
business_parking.df <- data.frame("business_id" = attributes_df$business_id, "Parking.Garage" = numeric(n_row), "Parking.Street" = numeric(n_row), "Parking.Validated" = numeric(n_row), "Parking.Lot" = numeric(n_row), "Parking.Valet" = numeric(n_row))
flag = !is.na(temp)

for(i in 1:n_row) {
  
  if(flag[i] && nrow(temp[[i]]) > 0) {
    entry = ifelse(temp[[i]] == "True", 1, 0) 
    business_parking.df[i,2:6] = entry
    # cat(" ")
    # cat(i)
  }
  else {
    entry = list(NA,NA,NA,NA,NA)
    business_parking.df[i,2:6] = entry
  }
}
attributes_df = inner_join(attributes_df, business_parking.df, by = "business_id") %>% select(-BusinessParking)

rm(list = "temp")

# rm(list = ls()) 

```


```{r}

toronoto_reviews_attrs_extracted = inner_join(toronoto_reviews_filtered_users.df, attributes_df, by = "business_id") %>% select(-attributes)


# Filter businesses based on the number of reviews they have
# K = 50
filter_business_id = toronoto_reviews_attrs_extracted %>%  filter(business_review_count >= 50) %>%
  select(business_id) %>% unlist  

toronoto_reviews_attrs_extracted = toronoto_reviews_attrs_extracted %>% filter(business_id %in% filter_business_id)   
toronoto_reviews_attrs_extracted = toronoto_reviews_attrs_extracted %>% select(business_id, categories, user_id, text, RestaurantsPriceRange2  , BikeParking, Parking.Garage, Parking.Street, Parking.Validated,Parking.Lot, Parking.Valet, RestaurantsTakeOut, GoodForKids, OutdoorSeating, RestaurantsGoodForGroups, RestaurantsReservations, RestaurantsDelivery, WiFi)

write.csv(x = toronoto_reviews_attrs_extracted, file = "toronto_filtered_reviews_all_cat.csv")

```


APPENDIX

Explore distribution of review_count for all users
```{r}
names(tip.df)
names(user.df)
quantile(user.df$review_count, probs = 0.85) 
# user.df_truncated = dplyr::filter(user.df, review_count >= 20)
```

Saving business_id of Vegas and Toronto 
```{r}
# saveRDS(list("vegas" = business_id_vegas, "toronto" = business_id_toronto), file = "/home/nitesh-jaswal/Study/Search/Project/city_business_id.RDS")
# saveRDS(business.df, file = "/home/nitesh-jaswal/Study/Search/Project/business.RDS")
# saveRDS(review.df, file = "/home/nitesh-jaswal/Study/Search/Project/review.RDS")
# 
# truncated_review_df = inner_join(filter(business.df, city == "Toronto"), review.df , by = "business_id")
# saveRDS(truncated_review_df, file = "/home/nitesh-jaswal/Study/Search/Project/toronoto_reviews_unfiltered_users.RDS")
saveRDS(toronoto_reviews_filtered_users.df, "/home/nitesh-jaswal/Study/Search/Project/toronoto_reviews_filtered_users.RDS")

rm(list = c("attribtues_df", "temp", "toronoto_reviews_attrs_extracted", "toronoto_reviews_filtered_users.df"))
```


